\subsection{Problem Statement}
\paragraph{}
I believe that there is a problem in the area of elearning, where there are not enough resources available online to convince teachers to use online applications, and the ones that are available are not of a high enough quality. For those reasons, teachers are not being as effective as they could be. I think that the following problems could be fixed with a software application:
\begin{itemize}
	\item A course could be created once one year, and used again with minimal changes to the course (probably changing the dates, but that's about it).
	\item Hard copies would not be needed (or at the very least, soft copies would be available). Coming from a student, this is extremely useful, because on many occasions, I have been on both ends of the problem, losing hard copies, and having friends ask me to scan my hard copies.
	\item Teachers wouldn't have to carry round any paper with them - assignments could be submitted online, meaning there is no massive pile of paper and no excuses from students about losing their assignments, or wanting to print it out on the day.
	\item Students can hand in assignments from home, which helps if they are away on the day.
	\item Teachers can store all the marks for the student online, and can view statistics about them at the click of a button. They could get the yearly marks for a student in a single click, for example.
	\item Especially in the case of subjects such as SDD, often there are programs which are marked by the teacher manually, but could be automarked.
	\item Current methods for recording marks online only tell you the marks as a whole. For example, in this project, we get marked on different parts of the project, such as a gantt chart and pseudocode. A better online system could solve that problem.
\end{itemize}